Categorical Predictor Embeddings in Actuarial Modeling

### 2021-04-03 manuscript/manuscript.Rmd

The working example for our experiments is as follows: Given a set of claim characteristics, we predict the losses paid 
on the property coverage of the policy. The data we use comes from the National Flood Insurance Program (NFIP) and is 
made available by the OpenFEMA initiative 
of the Federal Emergency Management Agency (FEMA)[^9]. Two datasets are made available by OpenFEMA: A policies dataset 
with exposure information, and a claims dataset with claims transactions, including paid amounts. Because there is no 
way to associate records of the two datasets, we are limited to fitting severity models on the claims dataset. While 
the 
complete dataset contains over two million transactions, for the purposes of our experiments we limit ourselves to data 
from 2000 to August 2019, which amounts to approximately 1.4 million claims. The dataset can be downloaded from 
Cellar[^10] The dataset includes a rich variety of variables, from occupancy type to coarse coordinates. For our 
models, 
we work with a few selected variables that represent continuous and discrete variables of low and high cardinalities, 
which we list in Table \@ref(tab:variables)

@@

For Model 2, we build a feedforward neural network, whose architecture is shown in Figure \@ref(fig:nn-1). 
The categorical inputs go through one-dimensional embedding
layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
have been normalized in data pre-processing, before being passed through a feedforward layer (with ReLU activation)
 to obtain a scalar
value between 0 and 1, as constrained by a sigmoid output activation. This scalar output represents the proportion of
coverage amount that is paid out, so we multiply it by the unnormalized dollar amount of the coverage amount to obtain
our prediction of the claims paid.

>>>>

The working example for our experiments is as follows: Given a set of claim characteristics, we predict the losses paid 
on the property coverage of the policy. The data we use comes from the National Flood Insurance Program (NFIP) and is 
made available by the OpenFEMA initiative 
of the Federal Emergency Management Agency (FEMA)[^9]. Two datasets are made available by OpenFEMA: A policies dataset 
with exposure information, and a claims dataset with claims transactions, including paid amounts. Because there is no 
way to associate records of the two datasets, we are limited to fitting severity models on the claims dataset. While 
the 
complete dataset contains over two million transactions, for the purposes of our experiments, we limit ourselves to 
data from 2000 to August 2019 and further subsample 100K data points to make experiments feasiable on a CPU.
 The dataset can be downloaded from 
Cellar[^10] The dataset includes a rich variety of variables, from occupancy type to coarse coordinates. For our 
models, 
we work with a few selected variables that represent continuous and discrete variables of low and high cardinalities, 
which we list in Table \@ref(tab:variables)

@@

For Model 2, we build a feedforward neural network, whose architecture is shown in Figure \@ref(fig:nn-1). 
The categorical inputs go through one-dimensional embedding
layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
have been normalized in data pre-processing, before being passed through a feedforward layer (with 8 hidden units 
and ReLU activation)
 to obtain a scalar
value between 0 and 1, as constrained by a sigmoid output activation. This scalar output represents the proportion of
coverage amount that is paid out, so we multiply it by the unnormalized dollar amount of the coverage amount to obtain
our prediction of the claims paid, which we evaluate using the mean squared error (MSE) loss function.
